% This project report describes the development of a C compiler extension based on the Procedural-Parametric Paradigm, a programming paradigm that enables the definition of parametric types and functions.
% The extension has been implemented using a source-to-source translator written in C.
% The report will include an experimental evaluation of the extension compared to other compilation approaches and syntactic variations, using metrics such as compilation time, code size, and extension effort.
% Overall, the extension offers a means of enhancing C with advanced features while preserving the performance benefits of the language.

This report describes the development of an extension for the C compiler based on the procedural-parametric programming paradigm. The extension enables the use of parametric types and functions in the C language, providing new capabilities for developers.
The report includes a detailed explanation of the procedural-parametric paradigm, covering its concepts and principles of operation. It also discusses the implementation of the extension using a C-based compiler.
It is important to note that the developed compiler works on the GNU+Linux platform and leverages advanced features such as constructors. These features allow for expanding the capabilities of the C language while maintaining its high performance.
The report targets developers and compiler specialists interested in exploring new programming paradigms and extending the C language. It provides a comprehensive description of the development process and serves as a guide for utilizing the developed extension in practical projects.
